Live Functional Programming with Typed Holes

### 2018-02-08 intro.tex
minor

In live programming, we expect that programs will generally have holes
in both terms and types (CITE?); however, to understand the mechanisms
of \HazelnutLive, it is instructive to imagine situations where the
only holes or in terms, or in types.
%
  When we only use type holes (not common in live programming, AFAIK),
  we recover gradual typing and do not need indeterminate forms
  (except for cast errors, which we classify this way).  
  % 
  When we only use expression holes, we do not need type casts, or
  the other dynamic mechanisms of gradual typing.

>>>>

In live programming, we expect that programs will generally have holes
in both terms and types (CITE?); however, to understand the mechanisms
of \HazelnutLive, it is instructive to imagine situations where the
only holes are in terms, or are in types.
%
When we only use expression holes and no type holes, we do not need
type casts, or the other dynamic mechanisms of gradual typing.
% 
When we only use type holes, we recover gradual typing and do not need
indeterminate forms (except for cast errors, which we classify this
way).
